Autonomous Oceanographic Sampling Designs using Excursion Sets for Multivariate Gaussian random fields

### 2020-05-29 ans_to_reviewers/answers-to-reviewers.tex

\item “joint excursion sets” in the title would be a turnoff for most statisticians. Having read the paper pretty carefully I still am not sure why they are so labelled.\par
\reply: We avoid the term' joint excursion sets' in the revised version. Instead we have introduced a mo more general random sets notation, but link to the ES for temperature and salinity whenever it is appropriate to exemplify concepts and show results.

@@

\vspace{1em}

\item Why on page 13 were those particular values chosen for the means $\mu$? Would a different choice have made a difference?\par

\reply: Preliminary runs set these trends. In a larger scale, one could here use ocean model inputs or satellite data.

\item I don’t think Figure 3 conveys too much additional benefit and eliminating it for space might be considered.\par

\reply: We removed this Figure. It took much space and it is sufficient to explain the optimal design in text as we did. 
\vspace{1em}

\item Why are the ES’s called ”excursion sets? Why excursion probabilities?\par

\reply: The revised Section 3 contains a general formulation for random sets, which is then exemplified by our excursion sets for the multivariate process. In the Introduction we motivate the excursion set for multivariate processes for this application, because it is important to find zones with joint high values of many variables. In the revised version we believe that the sets are introduced both more in the line with the practical application as well as for statistical novelty.
\vspace{1em}

\item I did not spot a definition for the “waypoint graph” a phrase used several times in the paper. Again points to the need to identify the audience. I doubt that most statisticians would know that phrase.\par
\reply: TO DO. Clarify. 
\vspace{1em}

\item In statistics journals, random variables are commonly labelled by Roman characters e.g. Z, parameters in Greek e.g. $\xi$. I realize that in other scientific domains that distinction is not always made but I do recommend the change if the paper is to appear in a stats journal.\par

\reply: We use $Z$ in the revised version.
\vspace{1em}

\item There is not much of novelty in the Gaussian Process theory used in the paper- its pretty much standard. I suggest that the derivations stated in detail be summarized by just the results. Statisticians will know these things and users will not care.\par
\reply: We collapsed the previous sections 3, 4 and 5 to one new section 3 containing the statistical novelty on EIBV closed-form expressions. The proofs are in a new Appendix.

@@

\begin{answers}
\item{\revcom : }\label{r2c1}

I know very little about the AUVs you discuss, and I suspect many of your readers will be in a similar position. Additional contextual information would be helpful

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[2.1.1] What sort of onboard computing do they have? It may not be something like an Intel 2.1 GHz, 4-thread processor, but a more informative description of something most readers relate to would be helpful. Similar information related to RAM and hard drive space would be helpful. What are the computational limits of these machines?\par

\reply: We have added more information about AUVs and their computational capabilities in Section 2.1 (Background on Ocean Processes and Observations) to address this. 
\begin{quote}
The AUVs, see Fig. 9, considered here operate at $1$-$3$ m/s in the upper water column, where they are free to move in six degrees of freedom (6 DOF). The in-water operation time capacity depends on survey speed, payload sensors and navigation. Generally this amounts to 8-24 hrs. operation for smaller crafts, and 24-48 hrs. for larger crafts. AUVs have limited computational capacity, as they typically use single-board computers (SBCs), like the Raspberry Pi or a multicore GPU NVIDIA Jetson TX1 (quad-core 1.91 GHz 64-bit ARM machine, a 2-MB L2 shared cache, and 4 GB of 1600 MHz DRAM) to do computation. 
\end{quote}
\vspace{1em}

\item[2.1.2] How long do the AUVs typically explore in one go? Is there a minimum/maximum time?\par

\reply: Maximum speed and payload are limiting for coverage. Generally this amounts to 8-24 hrs. operation for smaller crafts, and 24-48 hrs. for larger crafts. Time constraints for operations are typically related to costs of ship time and man-hours during operation. This information is contained in the changes made in point 2.1.1 above. 
\vspace{1em}

\item[2.1.3] What kind of movements can the AUVs make? Chess-like moves (horizontal, vertical, diagonal)?\par

\reply: AUVs are free to move in 6 degrees of freedom on the triangulated graph. They are essentially flying under water. However, one usually always proceed forward while pitching up and down. We have clarified this in the updated section shown in point 2.1.1. This is also shown in some of the figures (Fig.1 and Fig. 4) as well as the waypoint graph. 
\vspace{1em}

\item[2.1.4] Is there a minimum/maximum number of points you want to sample?\par

\reply: The coverage available is usually limited on battery capacity, which also determines the maximum number of points to sample. The important question here is "How do one prioritize the correct points to visit?", which is central to the development of the IBV and the application shown in the paper. 
\vspace{1em}

\item[2.1.5] What is the size of the grid that is typically considered? i.e., what is a typical value of $n$ in Eq.(9)?\par

\reply: The waypoint grid size $n$ should be small enough to resolve the process that is of interest and to avoid aliasing. A guiding rule of thumb provided by the the Nyquist theorem is to sample at least twice in time for the shortest significant record period, and twice in space for the shortest significant length to either resolve or eliminate (by filtering) scales of oceanic variability shorter than those being studied. In practice, this means mapping at an adequate spatial resolution faster than significant changes – in the phenomena – occur. 
\vspace{1em}

\item[2.1.6] Does the AUV use a selection algorithm from the very beginning or is there a minimum number of initial measurements that are made before the optimization algorithm begins?\par

\reply: As is common in such field trials with AUVs, we gathered data in an initial run that also tests the depth and bearings navigation systems. From this data, the model parameters were tuned and the AUV conducted adaptive sampling using the optimization strategy.
\vspace{1em}

@@

\end{itemize}

\item{\revcom :}\label{r2c2}

p. 9, Eq. (8): the dependency on $\bx$ and $\bx'$ has been omitted for some of the parameters without mention. Or are the parameters constant across locations?

\reply: In the revised version the notation has been improved.

@@

\item{\revcom :}\label{r2c3}

p. 9, How reasonable is the assumption of stationary and isotropic random fields? You may be limited by the computational abilities of the AUVs so that more complex models are computationally infeasible. That is a valid reason to choose a simpler, less accurate model. I’m just wondering if that is the reason here.

\reply: We agree that this is a simplified model. However, one would need high-resolution ocean model data or satellite information to fit a more complex model. But in the accompanying code we run cases with more complex covariances, so the interested user can test if / how it matters for the design. We believe spatio-temporal models would be a very interesting next step and present that as further work.

@@

\item{\revcom  :}\label{r2c4}

p. 9, Eq. (10). Are the temperature and salinity processes at a specific location effectively independent of one another? (I truly don’t know). That is what is implied by Eq. (10).

\reply: In our setting the temperature and salinity data are from different sensors and it is naturally to say they are conditionally independent measurements. That said, for other measurements, they might be extracted or processed from common sensor readings and would then be conditionally dependent. We mentioned this briefly in the data model description.

@@

\item{\revcom :}\label{r2c5}

p. 9, Eq. (11). The form of the equation is reminiscent of the Sherman-Morrison-Woodbury solution for fixed-rank kriging. $\bSigma$ may not be small here, but I wonder if there may be a computational advantage to considering an alternative computational solution.  See e.g., Cressie, N. and Johannesson, G. (2008), Fixed rank kriging for very large spatial data sets. Journal of the Royal Statistical Society: Series B (Statistical Methodology), 70: 209-226. doi:10.1111/j.1467-9868.2007.00633.x.

\reply: Only the surface is considered here, so computational requirements are not mainly driven by the size of the domain, but rather by the number of combinations for sampling designs (computational complexity). No 3D with depth, which would require simplified spatial models like fixed-rank-kriging or similar approaches.

@@

\item{\revcom  :}\label{r2c6}

p. 9, Eq. (13). Why does $\bm$ have a distribution before seeing the data? I can see how $\bm(\by)$ would have a distribution since it depends on $\by$. It almost feels Bayesian, but nothing indicates that this analysis is being pursued from a Bayesian perspective. Why is it valid for $\bm$ to have a distribution prior to seeing data?

\reply: We have generalized the closed-form solutions. (See point 2 at the start of reply letter.) The main body should contain results of general interest as well as provide insight about the statistical novelty. The proofs are now in Appendix with a succinct notation.

@@

\item{\revcom :}\label{r2c7}

p. 11, Eq. (17). I’m not understanding the advantage to conditioning on $\bm$ instead of $\by$? $\bm$ is a function of $\by$. The probability is the same two-dimensional integral either way. It seems to be related to the standardization that results in $\bZ$? Please clarify.

\reply: We have generalized the closed-form solutions. (See reply above.)

@@

\reply: We have generalized the closed-form solutions. (See reply above.)

\item{\revcom :}\label{r2c9}

p. 11, Is it purely for stylistic reasons that $P(\xi_T(\bx) \leq t_T, \xi_S(\bx) \leq t_S |\bm)P(\xi_T(\bx) \leq t_T, \xi_S(\bx) \leq t_S |\bm)$ isn’t written as $P(\xi_T(\bx) \leq t_T, \xi_S(\bx) \leq t_S |\bm)^2$? It seems to be a more natural way of expanding Eq. (18).

\reply: We have generalized the closed-form solutions. (See above.)

@@

\reply: We have generalized the closed-form solutions. (See reply above.)

\item{\revcom :}\label{r2c12}

This method relies on computing the marginal probabilities in each grid cell. This is computationally convenient and is likely required because of the limited computing power of the AUVs. However, the optimization should technically be performed with respect to the joint distribution across all grid cells. While the context may not allow this in practice, it would be helpful to get an idea of how much error is introduced by this approximation. I recommend creating a small but realistic-as-feasible simulation study comparing the accuracy of the probabilities, a comparison of the computational expense, and examining if/how navigation decisions change based on whether one uses the marginal/joint computations.

\reply: In the revised version we provide closed-form solutions to expected uncertainty reduction on volumes of random sets. However, for real-world application this involves many more terms in the evaluation criteria, so for the application, we still used marginals.

@@

\begin{quote}
-Don’t worry about the paths but focus on the nodes visited. Represent each node using a circle or hexagon.\par
-Make the node shading darker depending on whether that node is visited in a
simulation. Nodes with no visits would be white. Nodes with 100 visits would be black.\par
-The true excursion set is a random variable, but it would be informative to overlay the
average position of the excursion set over each of the panels so the reader can see how
the simulated AUV moves back and forth across the excursion set.
\end{quote}

\reply: TO DO

\item{\revcom :}\label{r2c14}

While the context does not allow full reproducibility of the paper results, no implementation details are provided. What software was used to perform the bulk of analysis? Are there scripts available that can be adapted by others for similar purposes? Please provide resources for the practical implementation of the methodology discussed in the paper.

\reply: Code is improved in the revision and provided for open-source usage: LINK

@@

\item{\revcom: Minor comments}\label{r2cminor}

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[2.15.1] “closed-form” is sometimes written as “closed-form” (e.g., p. 7, p. 18)

\reply: Now consistent with 'closed-form'.

@@

\begin{answers}

\item{\revcom - Major 1:}\label{r3c1}

I think this is an interesting paper. The paper is well written, 
and the authors have motivated the application well. 
The authors indicate several paths forward for work in this area, which I think pose interesting questions. They may want to elaborate a bit more on those.

\reply: We elaborated on space-time applications \cite{sigrist2015stochastic,richardson2017sparsity}. TO DO: 
More complex sampling Look-ahead, going further. 3D sampling, requiring more computationally efficient spatial statistical models.

@@

\reply: This is changed in revised version.

\item{\revcom - Major 2:}\label{r3c3}

Figure 4: Why not show excursion probabilities for, say, myopic selection as well?

\reply: We show EPs for myopic selection. Also, the accompanying code provides more cases.
